---
title: "DataProductFinalProject"
author: "Richard Yeow"
date: "April 22, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the Shiny App

This is the Shiny App which will show you the average temperature for a particular month.



## Air Quality data

```{r, echo=TRUE, comment=""}
head(airquality)
str(airquality)
```

## Air Quality data documentation
**Description**

Daily air quality measurements in New York, May to September 1973.

**Format**

A data frame with 154 observations on 6 variables.

- [,1]	Ozone	 numeric	 Ozone (ppb)
- [,2]	Solar.R	 numeric	 Solar R (lang)
- [,3]	Wind	 numeric	 Wind (mph)
- [,4]	Temp	 numeric	 Temperature (degrees F)
- [,5]	Month	 numeric	 Month (1--12)
- [,6]	Day	 numeric	 Day of month (1--31)


## Slide with Plot
```{r, echo=FALSE, message=FALSE}
library(plotly)
```
```{r, warning=FALSE}       
plot_ly(airquality, x = ~Month, y = ~Temp, color = ~Temp, type = "scatter", mode = "lines")
```

